format

### 2021-05-07 log_reg_analysis.Rmd
add PCA

## Variable correlations
```{r correlations, fig.show = "hold", out.width = "50%", fig.height = 12, fig.width = 15}

>>>>

## PCA & variable correlations
```{r pca}

library(factoextra)

# convert tibble to df
df_hbox_voi_df <- df_hbox_log_voi %>% dplyr::select(-Status) %>% as.data.frame() 
rownames(df_hbox_voi_df) <- df_hbox_impute %>% dplyr::filter(Status != "HV") %>% .$subject_id

# compute PCA
my_pca <- prcomp(df_hbox_voi_df, scale = TRUE)

# define groups
groups <- as.factor(df_hbox_log_voi$Status)

# Eigenvalues
pca_eig_val <- get_eigenvalue(my_pca)

# two data frames for plotting
df_vars <- my_pca$rotation %>% as_tibble() %>% mutate(variable = rownames(my_pca$rotation))
df_pnts <- my_pca$x %>% as_tibble() %>% mutate(group = groups)

# plot

library(ggpubr)
library(ggrepel)

  # plot patients
  ggplot() +
  geom_point(data = df_pnts, mapping = aes(x = PC1, y = PC2, color = group), 
             size = 3) +
  stat_conf_ellipse(data = df_pnts, mapping = aes(x = PC1, y = PC2, color = group, fill = group),
                    level = 0.95, npoint = 100, bary = TRUE, alpha = 0.1, geom = "polygon") +
  stat_mean(data = df_pnts, mapping = aes(x = PC1, y = PC2, color = group, shape = group),
            na.rm = FALSE) +

  # plot variables
  geom_point(data = df_vars, aes(x = PC1*10, y = PC2*10)) +
  geom_text_repel(data = df_vars, aes(x = PC1*10, y = PC2*10, label = variable, size = 10), show.legend = FALSE) +
  geom_segment(data = df_vars, aes(x = 0, y = 0, xend = PC1*10, yend = PC2*10), arrow = arrow()) +

  # draw lines
  geom_vline(xintercept = 0, lty = 2, color = "black") +
  geom_hline(yintercept = 0, lty = 2, color = "black") +

  # design
  xlab(paste0("PC1: ", round(pca_eig_val$variance.percent[1], 2), "% of variance")) +
  ylab(paste0("PC1: ", round(pca_eig_val$variance.percent[2], 2), "% of variance")) +

  ggtitle("PCA") +
  theme_bw()

```{r correlations, fig.show = "hold", out.width = "50%", fig.height = 12, fig.width = 15}
